Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip0.tex
Fix binding dfn for PiMeasure

\begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
	Let $\PMeasureStar$ be a cheating $\BQP$ prover for $\PiMeasure$.
	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
	$\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$.
	Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
	the verifier's outputs on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
\end{lemma}

@@

	Protocol:
	\begin{enumerate}
		\item \label{step:naive1} The verifier choose a $XZ$-measurement $h$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
		\item \label{step:naive2} The prover prepares $\rho$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
		If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
		If it's a Hadamard round, the verifier obtains $v$.
		\item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
			on inputs $1^\lambda$, $1^{1/\varepsilon}$, $x$, $h$, and $v$. \Ethan{So many inputs... Should the verifier keep internal states instead?}
	\end{enumerate}
\end{protocol}

@@

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$ as in \stepref{naive1} of $\PiNaive$
	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
		It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$ as in \stepref{measure2} of $\PiMeasure$.
		It sends $\vec{y}$ to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

>>>>

\begin{lemma}\label{lem:urmila-binding}[binding property of Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
	Let $\PMeasureStar$ be a $\BQP$ cheating  prover for $\PiMeasure$ and $\lambda$ be the security parameter. Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
\iffalse	
	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
	$\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$.
	Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
	the verifier's outputs on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
\fi
\end{lemma}

@@

	Protocol:
	\begin{enumerate}
		\item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
		\item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
		\item \label{step:urmila-in-naive} The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
		If it's a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
		If it's a Hadamard round, the verifier obtains $v$.
		\item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$

	\end{enumerate}
\end{protocol}

@@

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$
	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
		It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$ as in \stepref{measure2} of $\PiMeasure$.
		It sends $\vec{y}$ to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}
